Fourmile Calibrations

### 2022-12-28 calibration_output.Rmd
updating cal results for outlet only

params <- read_csv('calruns_params.csv') %>%
  drop_na()

@@

params <- params %>%
  mutate(input_data = case_when(
    grepl('station', run) ~ 'station',
    grepl('grid', run) ~ 'grid'
  )) %>%
  mutate(year_missing_almost = gsub('station_|grid_', '', run)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  select(-c(year_missing_almost)) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes') %>%
  mutate(value = as.numeric(value),
         param = as.factor(param))

@@

## Hydrograph

```{r hydrographs, echo = F}
flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s')

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line()

ggplotly(q)

@@

## Overall KGE

@@

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling(full_width = F)

@@

flow_year <- flow %>%
  mutate(WY = calcWaterYear(date)) %>%
  group_by(WY) %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'WY', values_from = 'kge')

flow_kge %>%
  kable(.) %>%
  kable_styling()

flow_plot <- flow_year %>%
  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
  mutate(WY = as.factor(WY))

kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
  theme_bw()

ggplotly(kge_plot_wy)

@@

plot_kge <- function(wateryear) {
  flow_plot %>%
    filter(WY == wateryear) %>%
    ggplot(aes(x = model_run,
               y = kge)) + 
    geom_col() + 
    ggtitle(wateryear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(flow_plot$WY)

lapply(name, plot_kge)

@@

>>>>

# params <- read_csv('calruns_params.csv') %>%
#   drop_na()

@@

# params <- params %>%
#   mutate(input_data = case_when(
#     grepl('station', run) ~ 'station',
#     grepl('grid', run) ~ 'grid'
#   )) %>%
#   mutate(year_missing_almost = gsub('station_|grid_', '', run)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   select(-c(year_missing_almost)) %>%
#   filter(!param == 'locGrw',
#          !param == 'tempRes') %>%
#   mutate(value = as.numeric(value),
#          param = as.factor(param))

# write_csv(params, 'paramsnew.csv')

params <- read_csv('paramsnew.csv') %>%
  mutate(value = as.numeric(value),
         param = as.factor(param))

@@

### Density plots: station vs. grid

```{r density plots, echo = F}

mean_params <- params %>%
  group_by(param, input_data) %>%
  summarize(mean = mean(value))

plotdens_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = value,
               fill = input_data, 
               color = input_data)) + 
    geom_density(alpha=0.4) +
    geom_vline(data=filter(mean_params, param == param_name), 
               aes(xintercept=mean, color=input_data),
             linetype="dashed", size=0.75) +
    ggtitle(param_name) +
    theme_bw()
}

lapply(name, plotdens_params)

@@

## Outlet results

### Hydrograph (outlet)

```{r hydrographs, echo = F}
# flow <- read_csv('discharge_all.csv') %>%
#   replace(.==-9999, NA)
# 
# 
# flow_pivot <- flow %>%
#   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
#   mutate(WY = as.factor(calcWaterYear(date)))
#   
# 
# q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
#   geom_line()
# 
# ggplotly(q)

### Hydrograph by WY

```{r wy hydrographs, echo = F}

# plotq_wy <- function(wateryear) {
#   {flow_pivot %>%
#     filter(WY == wateryear) %>%
#     ggplot(aes(x = date,
#                y = q_m3s,
#                color = cal_run)) + 
#     geom_line() + 
#     ggtitle(wateryear) +
#     theme_bw()} %>%
#     ggplotly()
#   
# }
# 
# name <- levels(flow_pivot$WY)
# 
# try <- lapply(name, plotq_wy)
# 
# htmltools::tagList(try)

### Overall KGE (outlet)

@@

# flow_kge_all <- flow %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)
# 
# flow_kge_all <- flow_kge_all %>%
#   pivot_longer(everything()) %>%
#   arrange(value)
# 
# kable(flow_kge_all) %>%
#   kable_styling(full_width = F)

@@

# flow_year <- flow %>%
#   mutate(WY = calcWaterYear(date)) %>%
#   group_by(WY) %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)
# 
# flow_kge <- flow_year %>%
#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
#   pivot_wider(names_from = 'WY', values_from = 'kge')
# 
# flow_kge %>%
#   kable(.) %>%
#   kable_styling()
# 
# 
# flow_plot <- flow_year %>%
#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
#   mutate(WY = as.factor(WY))
# 
# 
# kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
#   theme_bw()
# 
# ggplotly(kge_plot_wy)

@@

# plot_kge <- function(wateryear) {
#   flow_plot %>%
#     filter(WY == wateryear) %>%
#     ggplot(aes(x = model_run,
#                y = kge)) + 
#     geom_col() + 
#     ggtitle(wateryear) +
#     theme_bw() +
#     theme(axis.text.x = element_text(angle = 45, hjust=1))
# }
# 
# name <- levels(flow_plot$WY)
# 
# lapply(name, plot_kge)

@@

## Reach results

### Hydrograph by reach

```{r reach hydrographs, echo = F}

# reach <- read_csv('reach_all.csv') %>%
#   mutate(reach = as.factor(reach)) %>%
#   pivot_longer(!c(date, reach, WY), names_to = 'cal', values_to = 'q_cms')
# 
#   
# plotq_reach <- function(reach_name) {
#   {reach %>%
#     filter(reach == reach_name) %>%
#     ggplot(aes(x = date,
#                y = q_cms,
#                color = cal)) + 
#     geom_line() + 
#     ggtitle(reach_name) +
#     theme_bw()} %>%
#     ggplotly()
#   
# }
# 
# name <- levels(reach$reach)
# 
# try2 <- lapply(name, plotq_reach)
# 
# htmltools::tagList(try2)
# 
# ```
# 
# ### Overall KGE by reach
# 
# ```{r reach kge, echo = F}
# 
# reach_pivot <- reach %>%
#   pivot_wider(names_from = 'cal', values_from = 'q_cms') %>%
#   mutate(WY = as.factor(calcWaterYear(date)))
# 
# reach_kge_all <- reach_pivot %>%
#   group_by(reach) %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)
# 
# 
# reach_kge_all <- reach_kge_all %>%
#   pivot_longer(!reach, names_to = 'cal_runs', values_to = 'KGE') %>%
#   pivot_wider(names_from = 'reach', values_from = 'KGE')
# 
# 
# kable(reach_kge_all) %>%
#   kable_styling(full_width = F)
# 
# 
# obs_count <- reach_pivot %>%
#   select(obs, reach) %>%
#   drop_na() %>%
#   group_by(reach) %>%
#   summarize(count_obs = n())
# 
# kable(obs_count, caption = 'Streamflow observation count') %>%
#   kable_styling(full_width = F)
